On the Construction of Isomorphic Interpreters

### 2012-02-17 iso-int/iso-int.tex
pi

>>>>

%subcode{bnf} include main
% Combinators, c = iso | c (;) c | c (*) c | c (+) c
% Combinator Contexts, cc = [] | Fst cc c | Snd c cc 
%                  &|& LeftTimes cc c v | RightTimes c v cc 
%                  &|& LeftPlus cc c | RightPlus c cc 
% Values, v = () | (v, v) | L v | R v
%
% Machine states = <c, v, cc> | {[c, v, cc]}
% Start state = <c, v, []> 
% Stop State = {[c, v, []]}

%subcode{opsem} include main
% <iso, v, cc> &|-->& {[iso, iso(v), cc]}
% <c1(;)c2, v, cc> &|-->& <c1, v, Fst cc c2>
% {[c1, v, Fst cc c2]} &|-->& <c2, v, Snd c1 cc>
% {[c2, v, Snd c1 cc]} &|-->& {[ c1(;)c2, v, cc ]}
% <c1(+)c2, L v, cc> &|-->& <c1, v, LeftPlus cc c2>
% {[ c1, v, LeftPlus cc c2 ]} &|-->& {[c1 (+) c2, L v, cc ]}
% <c1(+)c2, R v, cc> &|-->& <c2, v, RightPlus c1 cc>
% {[ c2, v, RightPlus c1 cc ]} &|-->& {[c1 (+) c2, R v, cc ]}
% <c1(*)c2, (v1, v2), cc> &|-->& <c1, v1, LeftTimes cc c2 v2>
% {[ c1, v1, LeftTimes cc c2 v2 ]} &|-->& <c2, v2, RightTimes c1 v1 cc>
% {[ c2, v2, RightTimes c1 v1 cc ]} &|-->& {[ c1 (*) c2, (v1, v2), cc ]}

TODO : The real difficulty with this interpreter is to argue why it is
not full of undefined states. For instance, why the machines will
never reach stuck states such as {{<c1(+)c2, (), ..>}}.

The right way out of that is to make the type system of the abstract
machine rich enough that the structure of the abstract automatically
rules out this sort of thing.
